Consistent Polyhedral Surrogates via Embedding

### 2019-05-15 neurips-19/poly-embed.tex
comments in sec 6

\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro\raf{Jessie?} \\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proving (in)consistency via embeddings}
The above techniques allow us to evaluate and simplify some previous results in the literature.
\subsection{Top-$k$ loss}
Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.

@@

After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency... here I'm going by Yang's consistency.  I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.

>>>>

\title{Consistent Polyhedral Surrogates via Embedding}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro\raf{Jessie?} \\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proving (in)consistency via embeddings}
\raf{Notes about the story, partially to myself, partially to Jessie: I think we want to emphasize the proofs of consistency and inconsistency (as the section title reflects), but we also want to illustrate our constructive approach to finding a link.  Basically, most of these examples (except abstain) have the link built in (usually as the sign function, though slightly different for top-k), and they just work around it.  For abstain, we can give alternate link functions, and hopefully show that the L1-based link has a better calibration function.  For the others, it may suggest that it's worth thinking ``outside the box'' (HAH, genious...) for embeddings which are not the hypercube.}

The above techniques allow us to evaluate and simplify some previous results in the literature.
\subsection{Top-$k$ loss}
Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.

@@

After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency... here I'm going by Yang's consistency.  I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
\raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.  Take another look at Theorem 2.4 of the top-k paper.  Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.  I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.  In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.  Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.
